02_LH-SIP_Quantification

### 2022-03-29 02_LH-SIP_Quantification.Rmd
updated assimilation efficiency to use calculated values of a and sa

    # Explicitly define incubation parameters:
    # label is adjusted for the actual isotopic composition of the label within a specific terrain
    f_label = F_label_mn,
     # assimilation efficiency
    a = 0.6,
    # start time
    t0 = case_when(
      time_course == "0d -->" ~ 0,
      time_course == "3d -->" ~ 3),
    d_t = inc_time_d - t0, # change in time
    f_start = case_when(
      time_course == "0d -->" ~at2H_mn_zero,
      time_course == "3d -->" ~ at2H_mn_three),
    # use PAME-corrected 2F value
    f_t = `2F_alk`,
    # delta 2F: change in 2F enrichment over time t
    dF = case_when(
      f_t - f_start >= 0 ~ f_t - f_start,
      f_t - f_start < 0 ~ 0),
    # Calculate Turnover Rate in days from day 0 to 7 and 0 to 3
    u_d = calculate_turnover(
      a = a, # Assimilation efficiency
      FT = f_t, # 2F at time t (at%)
      F0 = f_start, # 2F at t0 (at%)
      FL = f_label, # 2F of label (at%)
      t = d_t # change in time
      ),
    # calculate generation time, converting negatives to zero
    gen_d = turnover_to_gen(u_d),

    # Calculate uncertainty in turnover rate
    su_d = calculate_sigma_mu(
      # Mean values:
      a = a,
      F_L = f_label,
      F_T = f_t,
      F_0 = f_start,
      t = d_t,
      # Uncertainties:
      sF_0 = F_0_at2H_se,
      sF_L = F_label_se,
      sF_T = 0,
      sa = 0
    )

>>>>

    # Explicitly define incubation parameters:
    # label is adjusted for the actual isotopic composition of the label within a specific terrain
    f_label = F_label_mn,
    # start time
    t0 = case_when(
      time_course == "0d -->" ~ 0,
      time_course == "3d -->" ~ 3),
    d_t = inc_time_d - t0, # change in time
    f_start = case_when(
      time_course == "0d -->" ~at2H_mn_zero,
      time_course == "3d -->" ~ at2H_mn_three),
    # use PAME-corrected 2F value
    f_t = `2F_alk`,
    # delta 2F: change in 2F enrichment over time t
    dF = case_when(
      f_t - f_start >= 0 ~ f_t - f_start,
      f_t - f_start < 0 ~ 0),
    # Calculate Turnover Rate in days from day 0 to 7 and 0 to 3
    u_d = calculate_turnover(
      a = a, # Assimilation efficiency defined in data reduction step
      FT = f_t, # 2F at time t (at%)
      F0 = f_start, # 2F at t0 (at%)
      FL = f_label, # 2F of label (at%)
      t = d_t # change in time
      ),
    # calculate generation time, converting negatives to zero
    gen_d = turnover_to_gen(u_d),

    # Calculate uncertainty in turnover rate
    su_d = calculate_sigma_mu(
      # Mean values:
      a = a,
      F_L = f_label,
      F_T = f_t,
      F_0 = f_start,
      t = d_t,
      # Uncertainties:
      sF_0 = F_0_at2H_se,
      sF_L = F_label_se,
      sF_T = 0,
      sa = sa
    )
